30June16 explant sups plate 3: MIG, RANTES, IL1ra

### 2016-07-12 30June16_plate_3_explant_sup.Rmd
Removed "below curve fit" data from plots

---
title: '30June16 explant sups plate 3: MIG, RANTES, IL1ra'
author: "Claire Levy"
date: "July 6, 2016"
output: github_document
---
This is an analysis of data from running our MSD plate 3 on some of HSV2 infected explant sup samples for Herpes P01. See explant_and_HVE_cell_sup_MSD_README for more on the different plates/analyte panels. This plate has the following analytes measured in each well

@@

#There is one sample where the concentration was below the fit curve range and the concentration is given as "NaN". In order for that point to appear on the plot, I am going to give those samples a value of "1"

NaNSamples<- explantDat %>%
  filter(Calc..Concentration == "NaN")%>%
  select(Sample, Detection.Range, Calc..Concentration)

explantDat <- explantDat %>%
  mutate(Calc..Concentration = ifelse(Calc..Concentration == "NaN", "1", Calc..Concentration))

@@

AvgConcExplantDat <- explantDat %>%
  group_by(Sample, Assay, Donor, Timepoint,Virus, Detection.Range)%>%
  summarize(avgConc = mean(Calc..Concentration))
```

@@

@@

```{r IL1-ra, echo=FALSE, warning=FALSE, message= FALSE}
## IL1-ra

@@

>>>>

---
title: '30June16 explant sups plate 3: MIG, RANTES, IL1ra'
author: "Claire Levy"
date: "July 6, 2016"
output: github_document
---
This is an analysis of data from running our MSD plate 3 on some of the HSV2 infected explant sup samples for Herpes P01. See "explant_and_HVE_cell_sup_MSD_README.txt"" for more on the different plates/analyte panels. This plate has the following analytes measured in each well

@@

#There is one sample where the concentration was below the fit curve range and the concentration is given as "NaN". This is because values can't be extrapolated below the curve. I am removing these data points.

explantDat <- explantDat %>%
  filter(Detection.Range != "Below Fit Curve Range")

@@

# AvgConcExplantDat <- explantDat %>%
#   group_by(Sample, Assay, Donor, Timepoint,Virus, Detection.Range)%>%
#   summarize(avgConc = mean(Calc..Concentration))
```

@@

Another way of looking at the data

```{r MIG alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = MIGexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  scale_shape_manual(values = c("Above Fit Curve Range" = 1, "In Detection Range" = 16))+

  facet_wrap(~Virus)+

@@

```{r RANTES alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = RANTESexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  facet_wrap(~Virus)+
  ggtitle("RANTES data")

```{r IL1-ra, echo=FALSE, warning=FALSE, message= FALSE}

@@

```{r IL1RA alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = IL1RAexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  facet_wrap(~Virus)+
  ggtitle("IL1RA data")
```
